---
title: "Lab 00 - Hello IDS!"
author: "Evelyn"
date: "`r Sys.Date(29/09)`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
install.packages("tidyverse")
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Evelyn", "Sadie", "Ruth"),
  github_username = c("evmulcahy", "sadie_mac", "brownruth3"), 
  colour = c("purple", "pink", "blue"),
  hobby = c("hockey", "netball", "bascketball"),
  favourite_number = c(9, 6, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Plots a bar graph with group github_username on the x-axis and favorite numbers on the y-axis. The bar graphs are filled with each group members respective favorite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github usernames", 
          y = "favorite numbers",
          title = "group members' information")
```

command labs gives the axises and graph a title

### Exercise 20

```{r new-bar-plot}

p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()

p2

```

each person has a different hobbie and increasing the data frame to the size of the course will only increase the number of variables on the x-axis
